A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-14 manuscript.Rmd
add rambling about preregistration

A preregistration is a tool that may help to increase the credibility of empirical results.

>>>>

A preregistration serves as a tool that may help to increase the credibility of empirical results.
Without getting lost in the meta scientific arguments for preregistration, we want to note two advantages.
First, a preregistration is an opportunity to carefully plan a study.
Gathering empirical data often requires enormous resources and better planning increases the chances that these efforts are worthwhile.
For us a good preregistration is the same as a good plan; the only difference is that a preregistration is made public beforehand.
Some [citation!] argue that preregistration can not fulfill its promise to reduce the false discovery rate of science, if we allow to deviate from them.
While such argument has some merits, we believe another advantage of preregistration is transparency.
If researchers deviate from their preregistration, they probably have good reason to do so, which means they have learned something from the process of conducting the study.
A preregistration, together with version control allows their readers to inform themselfs about these lessons learned.
